---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# textrar

The goal of textrar is to translate texts with TexTra easily.

https://mt-auto-minhon-mlt.ucri.jgn-x.jp/


## Installation

You can install from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
  # install.packages("remotes")
remotes::install_github("matutosi/textrar")
```

You can also install from CRAN:

```{r, eval = FALSE}
install.packages("textrar")
```

## Example

You can use `textra()` to translate texts with textra easily.

Store your credentials in the user `.Renviron` file, which
`usethis::edit_r_environ()` opens, and restart R.
Keeping them out of your scripts keeps them out of version control.

```
TEXTRA_API_KEY=your_api_key
TEXTRA_API_SECRET=your_api_secret
TEXTRA_NAME=your_login_id
```

```{r example, eval = FALSE}
library(textrar)

params <- gen_params()

text <- "Hello world"
translated <- textra(text, params, model = "transLM", from = "en", to = "it")
translated
 ## [1] "Ciao mondo"
```

You can also pass the credentials explicitly, for example when you keep
them somewhere else.

```{r example2, eval = FALSE}
key <- "abcdefghijklmnopqrstuvw01234567890abcdef1" # API key
secret <- "xyzabcdefghijklmnopqrstuvw012345"       # API secret
name <- "login_ID"                                 # login_ID
params <- gen_params(key = key, secret = secret, name = name)
```

## Citation

Toshikazu Matsumura (2024) textrar. Interface to TexTra from R. https://github.com/matutosi/textrar/
